\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Reman Buddhacharya} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{ +977-9761783411\\ Dallu, Kathamndu, Nepal 44600} 
\address{\href{mailto:remanbuddhacharya@gmail.com}{remanbuddhacharya@gmail.com} \\ \href{https://linkedin.com/in/reman-buddhacharya}{www.linkedin.com/in/reman-buddhacharya} \\ \href{https://remanbuddhacharya.com.np}{remanbuddhacharya.com.np}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Computer Science student exploring QA and automation, seeking software developer internship opportunities for Summer 2025.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Computer Applications}, National College of Computer Studies, Kathmandu \hfill {Expected 2026}\\
Relevant Coursework: Data Structures \& Algorithms, Database Systems, Web Development, Software Engineering.
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }

Programming Languages & PHP, JavaScript, Python, SQL, HTML, CSS \\
Testing \& Automation & Playwright, Test Automation Frameworks \\
DevOps \& Tools & Git, GitHub Actions, CI/CD, MySQL, PostgreSQL, Figma \\
Soft Skills & Problem-solving, Team collaboration, Communication, Test Planning \\


\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Full Stack Developer (Academic Project)} \hfill
 \begin{itemize}
    \itemsep -3pt {}
     \item Built comprehensive Gym Management System using PHP and MySQL with member tracking features.
     \item Developed Smart Expense Tracker with analytics achieving user satisfaction in testing.
    \item Collaborated on community projects and maintained multiple repositories on GitHub. 
    
 \end{itemize}
 \end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Gym Management System} { Built comprehensive fitness center management application using PHP and MySQL. Features member registration, subscription management, and financial reporting with secure authentication. Designed intuitive admin dashboard for streamlined operations. \href{https://github.com/RemonBuddhacharya/GymManagement}{(Github)}}

\item \textbf{Kharcha Track} {Smart Expense Tracker. Advanced personal finance management application with intelligent insights built using PHP framework. Features budget planning, expense categorization, and financial goal tracking with dynamic data visualization. 
\href{https://github.com/RemonBuddhacharya/kharcha-track}{(Github)}}

\item \textbf{E-commerce Test Automation Framework} {Developed a comprehensive test automation framework using Playwright and JavaScript for an e-commerce platform. Implemented data-driven testing with JSON fixtures, and CI/CD pipeline using GitHub Actions. Features include automated testing of user authentication, shopping cart operations, and product search functionality with parallel test execution capabilities. \href{https://github.com/RemonBuddhacharya/Ultima_QA}{(Github)}}

\end{rSection}


%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities} 
\begin{itemize}
    \item 	Active contributor to open-source projects on GitHub with multiple repositories showcasing web development skills and collaboration with other developers in the community.

    
    \item	Participate in local developer meetups and coding workshops to stay current with latest web development trends and technologies.
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Leadership} 
\begin{itemize}
    \item Project Lead for multiple personal development projects, successfully managing them from conception to deployment while maintaining high code quality standards and user satisfaction.
\end{itemize}


\end{rSection}


\end{document}
